Project-I by Group Sao Paulo

### 2015-11-02 report/paper.tex

\begin{abstract}
In this report, we study several linear method to compute regression and classification on two different datasets. For the regression part, we used k-means clustering to separate the data in three clusters. As the input matrix is ill-conditioned, we applied a PCA algorithm to reduce its dimensionality. We observe that the three methods are equivalent, with RMSE around $520$ for train and for test parts. For the classification part, we separate the data given their distribution along the dimensions of the input. WHICH ALGORITHM IS THE BEST; IDEA OF ERROR.
\end{abstract}

@@

Figure ~\ref{fig:reg_compareMethods} compares three regression methods with $\alpha = 0.25$ for the gradient descent and $\lambda = 100$ for ridge regression. We see that the three methods give equivalent results. This is surely the consequence of preprocessing the data with PCA, so that the input matrix is not ill conditioned.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=4in]{figures/comparisonReg.png}
	\caption{Boxplots of train and test RMSE for least-squares, least-square with gradient descent and ridge regression.}
	\label{fig:reg_compareMethods}
\end{figure}

@@

\section{Summary}
In this report, we analyse a regression and a classification dataset. We used k-means clustering and PCA to preprocess the regression data. We found that TODO.
We separated the classification data using a binary dimension that classify the data in two different distributions along the variable of the input data. We found that TODO.

>>>>

\begin{abstract}
In this report, we study several linear method to compute regression and classification on two different datasets. For the regression part, we used k-means clustering to separate the data in three clusters. As the input matrix is ill-conditioned, we applied a PCA algorithm to reduce its dimensionality. We observe that TODO. We obtained similar train and test RMSE around $520$. For the classification part, we separate the data given their distribution along the dimensions of the input. WHICH ALGORITHM IS THE BEST; IDEA OF ERROR.
\end{abstract}

@@

Figure ~\ref{fig:reg_compareMethods} compares three regression methods with $\alpha = 0.3$ for the gradient descent and $\lambda = 100$ for ridge regression. It is important to note that some outliers (11 for the train, 17 for the test) of least-squares method are not visible in this graph, as their RMSE is higher than $10^4$.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/comparisonReg.png}
	\caption{Boxplots of train and test RMSE for least-squares (LS), least-squares with gradient descent (LS-GD) and ridge regression (Ridge).}
	\label{fig:reg_compareMethods}
\end{figure}

The median train/test RMSE are respectively equal to $526/539$, $551/562$ and $526/524$ for least-squares, least-squares GD and ridge regression. We observe that least-squares GD has a high bias and a low variance compared to least-squares that has a lower bias and a higher variance.

@@

\section{Summary}
In this report, we analyse a regression and a classification dataset. We used k-means clustering and PCA to preprocess the regression data. We found that least-squares, least-squares with gradient descent and ridge regression TO DO.

We separated the classification data using a binary dimension that classify the data in two different distributions along the variable of the input data. We found that TODO.
